\begin{rubric}{Presentations}
\subrubric{Invited Talks and Seminars}
\entry*[2025] \textbf{Invited Panelist}. Cambridge Film Festival, Cambridge, UK. \textit{Title: Film Screening: Women+ Cancers Event.}
\entry*[2025] \textbf{Invited Workshop}. Cleveland Biomedical Training Alliance Conference. Cleveland, OH. \textit{Title: Building your Brand as a Biomedical Research Scientist.}
\entry*[2025] \textbf{Invited Talk}. Special Session: Mathematical Biology, JMM. Seattle, WA, USA.
\textit{Title: How Identity Can Guide Research: Topology, Biology, and Machine Learning for Cancer Research}
\entry*[2024] \textbf{Invited Talk}. Emerging Researchers in Mathematical Oncology: The MathOnco Subgroup Minisymposium. Society of Mathematical Biology. Seoul. Korea. (June) \par \textit{Title: Wearable Device Data as a Digital Biomarker in Cancer Patient Digital Twin Models.}
\entry*[2024] \textbf{Invited Talk}. Special Session: Mathematics of DNA and RNA, JMM. San Francisco, CA, USA. \par \textit{Title: Graph-based models of cancer evolution.}
\entry*[2023] \textbf{Department Seminar}. Mathematics, Cleveland State University, Cleveland, OH, USA. \par \textit{Title: Solving partial-differential equations for eco-evolutionary cancer models.}
\entry*[2023] \textbf{Invited Talk}. Special Session: Mathematics of DNA and RNA, JMM. Boston, MA, USA.
\entry*[2022] \textbf{Invited Talk}. Special Session: Mathematics of DNA and RNA, Joint Mathematics Meeting (JMM). \emph{(Online)}. 
\entry*[2021] \textbf{Invited Talk}. Society of Mathematical Biology. \emph{(Online)}.\par
\textit{Title: Evolutionary Control on Game Landscapes}



%
\subrubric{Contributed Talks}
\entry*[2024] \textbf{JMM} Contributed Paper Session on Algebraic Topology and Manifolds, II. San Francisco, CA, USA.\textit{Title: Topology and folds of fully enumerated, small on-lattice HP protein model}
\entry*[2024] \textbf{JMM} Special Session. Geometry and Topology of High-Dimensional Biomedical Data. San Francisco, CA, USA. \textit{Title:Topological data analysis for highly multiplexed tissue imaging.} 
\entry*[2023] \textbf{AACR Special Session:}  Translating Cancer Evolution and Data Science: The Next Frontier. Boston, MA. \textit{Title: Topology of the tumor microenvironment: The integration of imaging, modeling, and topological data analysis.}
\entry*[2023] \textbf{MathOnc2023}. Mathematical Oncology Meeting. Mayo Clinic, Phoenix, AZ. \par \textit{Title: De-coupling cell-intrinsic and cell-extrinsic effects to model and interpret drug-dependent evolutionary games}
\entry*[2022] \textbf{TMD22.} Trans Math Day 22 \emph{(Online).} \par \textit{Title: Eco-evolutionary effects in population dynamic models.}
\entry*[2022] \textbf{BAMM!22} Biology and Medicine in Mathematics 22. Virginia Commonwealth University, Richmond, VA
\entry*[2022] \textbf{AACR. }Evolutionary Dynamics in Carcinogenesis and Response to Therapy, Tampa, FL. 
\entry*[2021] \textbf{ISCMO'21. } International Symposium on Mathematical and Computational Oncology.\emph{(Online)}

%
\subrubric{Poster Presentations}
\entry*[2023] \textbf{AACR:}  Translating Cancer Evolution and Data Science: The Next Frontier. Boston, MA.
\entry*[2023] \textbf{Cleveland Clinic:}  LRI Research Day, Cleveland, OH.
\entry*[2022] \textbf{IMOX: Cancer Communities}. Integrated Mathematical Oncology Workshop X. Moffitt Cancer Center. Tampa, FL. 
\entry*[2022] \textbf{BAMM!22}. Biology and Medicine in Mathematics. Virginia Commonwealth University, Richmond, VA. \textit{CoOccurR.}
\entry*[2020] \textbf{AACR}. Annual Meeting '20 (Virtual). \emph{(Online)}
\entry*[2019] \textbf{EACR}. Cancer Genomics 2019, Cambridge, UK. 


\end{rubric}