\begin{rubric}{Research and Clinical Experience}
\subrubric{Clinical Trials}
\entry*[2025-]
\textbf{Co-Principal Investigator,} \textit{Orthopedic Oncology Remote Monitoring and Care}. Case Comprehensive Cancer Center, Cleveland, OH. \textbf{IRB Pending}
\entry*[2025-]
\textbf{Co-Principal Investigator,} \textit{Remote Monitoring for Phase I Cancer Trials}. Case Comprehensive Cancer Center, Cleveland, OH. \textbf{IRB Pending}
\entry*[2024-]
\textbf{Co-Principal Investigator,} \textit{Glioblastoma Remote Monitoring and Care}. Case Comprehensive Cancer Center, Cleveland, OH. \textbf{Enrolling, NCT06129760}. \url{https://classic.clinicaltrials.gov/ct2/show/NCT06129760}


%
\subrubric{Postdoctoral}
\entry*[2023-]%
	\textbf{Postdoctoral Research Fellow,} Taussig Cancer Institute, Cleveland Clinic.
     \par Department: \emph{Rose Ella Burkhardt Brain Tumor and Neuro-Oncology Center}. 
  \par Co-Department: \emph{Translational Hematology \& Oncology Research}
\par Award: \textbf{American Cancer Society Postdoctoral Research Fellowship.} 
 \par Topic(s): \emph{Remote Monitoring and Informatics for Predictive  Digital Twins in Glioblastoma}
 \par Advisor(s): \emph{Prof. Jacob Scott,  MD, DPhil \& Andrew Dhawan, MD, DPhil}

%
\entry*[01/2021-23]%
	\textbf{Postdoctoral Research Fellow,} Taussig Cancer Institute, Cleveland Clinic. 
         \par Department: \emph{Translational Hematology \& Oncology Research}.
        \par Co-Department: \emph{Department of Physics}, Case Western Reserve University, Cleveland, OH.
        \par Topic(s): \emph{Mathematical Models of Game Theory in Oncology}
        \par Advisor(s): \emph{Prof. Jacob Scott, MD, DPhil \& Prof. Mike Hinczewski, PhD}

\subrubric{Pre-doctoral}
\entry*[2014] \textbf{Summer Research Studentship,} Department of Planetary Physics, \par University of Oxford, Oxford, United Kingdom
\par Project: \emph{Analysis of Neptune's Cloud Structure}
\par Advisor: \emph{Prof. Patrick Irwin}
%
\entry*[2013] \textbf{Summer Research Studentship,} Department of Biophysics, \par University of Oxford, Oxford, United Kingdom
\par Project: \emph{Holographic Microscopy for 3D Particle Tracking}
\par Advisor: \emph{Prof. Richard Berry}
%
\end{rubric}