\begin{rubric}{Grants and Awards}
\subrubric{Grants and Fellowships}
\entry*[2025-2027]  \textbf{American Cancer Society Postdoctoral Fellowship} $\$150,000$ Principal Investigator. Cleveland Clinic, Cleveland, OH. \textit{Project: Integrating Free-Living Data into Digital Twin Models of Glioblastoma.}
\entry*[2021-23] \textbf{Velosano Pilot Grant.}  Key Personnel. Cleveland Clinic, Cleveland, OH. \par \textit{Project: Eco-evolutionary dynamics of lung cancer.}
\entry*[2016-2020] \textbf{Cancer Research UK Graduate Student Fellowship.} Cancer Research UK Cambridge Institute. University of Cambridge. Cambridge, UK.
\entry*[2014-15] \textbf{Summer Research Fellowship.} Department of Planetary Science. University of Oxford. Oxford, UK.
%
\subrubric{Awards}
\entry*[2024]  \textbf{LRI Postdoctoral Service and Leadership Award.} Cleveland Clinic Foundation, Cleveland, OH. 
\entry*[2024] \textbf{Janel Callon Outreach Award}. RiseUP Northeast Ohio. Cleveland, OH. 
\entry*[2023] \textbf{LRI Alumni Association Travel 
Award.} MathOnco23. Phoenix, AZ. 
\entry*[2022] \textbf{Travel award.} Biology and Medicine in Mathematics! 22. Richmond, VA. 
\entry*[2022] \textbf{Travel award.} Integrated Mathematical Oncology Workshop X. Moffitt Cancer Center. Tampa, FL. 
\entry*[2015] \textbf{Project award.} Most innovative MPhys Project. (\$100)
\par Department of Physics, University of Oxford, Oxford. 
\par \textit{Project: Genotype-phenotype space of HP protein folding models.}
\entry*[2015] \textbf{Project award.} Best overall MPhys Project. (\$250)
\par Department of Physics, University of Oxford, Oxford. 
\par \textit{Project: Genotype-phenotype space of HP protein folding models.}
\end{rubric}