\begin{rubric}{Mentoring Experience}
%
\subrubric{Graduate Students}
\entry*[2024-] \textbf{H. Kumar}, School of Medicine. Case Western Reserve University,  OH.
\par \textit{Project: Modeling patient oxygenation as a Markov process using continuous monitoring data from patients undergoing post-surgical monitoring.}
\entry*[2023-] \textbf{S. Patanavich}, School of Medicine. Case Western Reserve University,  OH.
\par \textit{Project: Clinical trial design for remote monitoring in glioblastoma.}
\entry*[2022-] \textbf{J.M. Gray}, Department of Physics. Case Western Reserve University, OH.\par
\textit{Project: Game interactions in spatial and range expansion tumor models.}
\entry*[2023-2024] \textbf{N. Latina}, Department of Genetics. Case Western Reserve University,  OH.
\par \textit{Project: Neural networks and data augmentation for human activity recognition.}
\entry*[2022-2024] \textbf{M. Reinius, MD}, Cancer Institute, University of Cambridge, Cambridge, UK.\par \textit{Project: Spatial metrics and topological data analysis for histopathology.}
\entry*[2022-2023] \textbf{B. Feng}, School of Medicine. Case Western Reserve University,  OH.
\par \textit{Project: Wearable device software for collecting remote monitoring data.}
\entry*[2022-2023] \textbf{G. Clarke}, Department of Neuroscience, Kings College London, London, UK. \par \textit{Project: Computational models of mutant ARPP aggregation in neurons.}
%
\subrubric{Undergraduate Students}
\entry*[2024-] \textbf{L. Jankowski}, Department of Biology. University of Arizona, AZ.
\par \textit{Project: Analysing feasibility of wearable monitoring and likelihood of detecting treatment response in cancer patients using the NIH All of Us Database.}
\entry*[2024-] \textbf{H. Simons}, Department of Computer Science. Cleveland State University, OH.
\par \textit{Project: Remote sensing for digital health biomarkers on Android platforms .}
\entry*[2024-] \textbf{A. Stacy}, Department of Physics. Case Western Reserve University,  OH.
\par \textit{Project: Sensing resistance evolution in the morbidostat under different treatment regimens.}
\entry*[2022-2023] \textbf{C. Nosrati}, Department of Mathematics. Case Western Reserve University,  OH.
\par \textit{Project: Game Theory in Models of Population Genetics.}
%
\subrubric{Highschool Students}
\entry*[2023-] \textbf{J. Joyce}, Engineering and Data Science. Rising Junior. Cleveland, OH
\par \textit{Project: Sensing resistance evolution in the morbidostat under different treatment regimens.}
\entry*[2022] \textbf{D. Suh}, Machine Learning and Data Science. Rising Senior, Cleveland, OH
\par \textit{Project: Machine learning for human activity recognition.}
\end{rubric}